---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```
# lemropendata

`lemropendata` is an R interface to the [LEMR Housing Monitor open data portal](https://data.lemr.ca/). The goal of the package is to help read data directly into R without needing to manually download it via the portal.

## Installation

You can install the development version from GitHub with:

``` r
devtools::install_github("purposeanalytics/lemr-open-data")
```

## Usage

In the portal, datasets are called **packages**. There is one for each region in the LEMR Housing Monitor. You can see a list of available packages by using `list_packages()`.

```{r list-packages-example, eval = FALSE}
library(lemropendata)
datasets <- list_packages()
packages
```

```{r list-packages-example-internal, echo = FALSE}
library(lemropendata)

datasets <- list_packages(token = NULL)

datasets
```

Within a package, there are a number of **resources**. Resources are the actual "data". the building or base layers in the tool.

We can filter down to the region of interest and then list the data within it using
`list_package_resources()`.

```{r list-to-app-layers-resources}
library(dplyr)

greater_toronto_area_data <- datasets %>%
  filter(title == "Greater Toronto Area / Grande région de Toronto") %>%
  list_package_resources()

greater_toronto_area_data
```

Finally (and most usefully!), you can download the actual data directly into R using `get_resource()`:

```{r get-resource}
greater_toronto_area_data %>%
  filter(name == "Building layer - Greater Toronto Area") %>%
  get_resource()
```
